\tool: A Multi-Mode BadUSB Device

### 2021-01-04 WOOT/Files/related_work.tex
related work v_1

\section{Related Work}
\label{sec:related_work}
\hongyi{Move the stuff about USB protocol to Background}\\
\outline{Attack based on USB 1.0, briefly}\\
\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
\outline{Attack survey table}\\
\outline{Attack or current works about USB Type-C}\\

In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
\subsection{USB Attack Security}
\hongyi{DO NOT COPY!}\textcolor{red}{USB 1.0\cite{usb10} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.} USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s). Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.

USB 2.0 protocol increased the speed of data transfer and it was also expended to include digit cameras. According to the protocol, the host recognises the peripherals through enumeration, and this gives attacked chance to cheat the host. BadUSB\cite{badusb} is going to attack host by modifying the devices' identify, re-flash the firmware to add more functionalities to the USB devices, for example, it can present malicious interfaces as a sample HID interfaces or work as a network adapter on a USB thumb driver. Other USB attacks, \cite{rubber}, \cite{usbdriver}, \cite{usbbypassing}, \cite{iseeyou} are also masquerading the USB protocol and provided illegal functionality interface to the host, taking advantage of the permissive trust model in USB whereby the host fully trust the devices connected. \cite{syzkaller} use the fact that the host's USB software stack generally expects devices with a standard USB protocol, with the help of fuzzing techniques using FaceDancer \cite{facedancer} and debuggers, it takes a number of vulnerabilities to the kernel-model. Furthermore, expect from the protocol related attack, the radio frequency based sensitive data stealing is another kind of attack, \cite{smartphone} , \cite{poweremi}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} work based on signal eavesdropping to attack during the data extraction, and \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.

As our best knowledge, attacks based on USB 3.0\cite{usb30} have not been discovered. In this work, we focus on attack based on USB 3.0 in the layer of transport\cite{sok}, which use the USB protocol to control the host or inject malicious command to the host connected with Type-C\cite{typec}, and streal the data trough it.

>>>>

\section{Related Work}
\label{sec:related_work}

In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.

\subsection{USB Attack Security}
While many USB based  attacks have been developed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transformation interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received. When the  protocol masquerading attack devices, e.g., Rubbery Ducky\cite{rubber}, \cite{rubberducky2020} and USBderivery\cite{usbdriver}, are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying. Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter. Due to the limitations of USB 2.0, it is impossible to handle the real-time screen information of the host, so only environment fitted commands or data will work in these scenarios.

In a similar way, \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host. Due to the limitation of functionality interface of devices for video transformation, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pause the execution processing in the inappropriate time.

Another kind of attacks for USB to exfiltrate data\cite{smartphone}\cite{poweremi} and \cite{usbdriver} is to eavesdrop signal to recovered the sensitive data at the physical layer. Even though the data, including the video data, could be recovered in this way, the attack for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
